Fail Faster

### 2025-03-21 paper/paper.tex
chart

We lay a path forward.
First, we show how to use \textit{multi-stage programming}, a classic technique for 
building fast DSLs “without regret”~\cn{}, to eliminate the overhead of 
many common generator abstractions. We refer to this approach as \name.
Second, we show that the source of entropy is an underappreciated factor in 
generator library design by isolating its run-time cost and demonstrating that 
substantial speedups are possible, while maintaining output equivalence.
These insights give a recipe for building generator libraries that marry high-level design
with low-level performance.

>>>>

We chart a path forward.
First, we show how to use \textit{multi-stage programming}, a classic technique for 
building fast DSLs “without regret”~\cn{}, to eliminate the overhead of 
many common generator abstractions. We refer to this approach as \name.
Second, we demonstrate that the source of entropy is an underappreciated design factor by 
isolating its runtime cost and showing that significant speedups can be achieved 
while preserving output equivalence.
These insights lay the groundwork for generator libraries that combine high-level 
design with low-level performance.
